Quantifying passive kelp rafting phenomena and connectivity of nearshore communities around the coast of South Africa through development of a 3D spectral numerical coastal-flow model

### 2020-08-05 thesis_chapter_1.Rmd
added to leeway section

An objects motion relative to the wind is sometimes referred to as "windage factors" or "leeway drift", and is difficult to accurately and empirically describe. The difficulty is due to accurate measurements needed for the current velocity, wind velocity, wave height and wave direction. The appropriate approaches to measuring the afprmentioned parameters have been detailed by @allen1999 and is dependent on the objects size and shape as well as the quality and quantity of data available to the modeler. Additionally, these factors do not act independently and instead influence one another, which compounds the complexity of calculating wind effects on drifting objects. To overcome this challenge, measurements of current and wind velocity, and wave height and direction are measured along the objects trajectory for a wide range of conditions.

>>>>

An objects motion relative to the wind is sometimes referred to as "windage factors" or "leeway drift", and is difficult to accurately and empirically describe. The difficulty is due to accurate measurements needed for the current velocity, wind velocity, wave height and wave direction. The appropriate approaches to measuring the afprmentioned parameters have been detailed by @allen1999 and is dependent on the objects size and shape as well as the quality and quantity of data available to the modeler. Additionally, these factors do not act independently and instead influence one another, which compounds the complexity of calculating wind effects on drifting objects. To overcome this challenge, measurements of current and wind velocity, and wave height and direction are measured along the objects trajectory for a wide range of conditions. Wind has been shown to be an important influencer on passive drifting objects in the ocean and much research has gone into understanding how to properly predict the effect of wind on an objects drift trajectory. Small objects respond almost linearly to changes in the wind speed [@Breivik2008]. The rule of thumb in trajectory modelling is to assume a linear relation between 10m wind speed and the objects motion relative to the water. In general, an object's motion through the ambient water masses (referred to as its slip, windage or leeway) is roughly inversely proportional to the immersion ratio. The inverse relationship to windage and immersion ration has been shown previously by @Geyer1989 and @oDonnel1997, and has been used in modelling shipping container trajectories. However, objects with complex shapes can be influenced substantially by crosswind motion. In addition, the relation between the crosswind motion and immersion ratio is not well understood and can vary greatly between objects [@Breivik2011].
